---
title: "FARS package"
author: "Chau Nam Ky Nguyen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The functions in this pacakage will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. This package contains following functions:

- make_filename
- fars_read
- fars_read_years
- fars_summarize_years
- fars_map_state

## Data Info

Data in this package ranges from 2013 to 2015. They are stored in three CSV files:

  * accident_2013.csv.bz2
  * accident_2014.csv.bz2
  * accident_2015.csv.bz2

For reading data user can use two functions `make_filename` to create a full path to a raw file, and `fars_read` to read the CSV file into the system.

```{r echo=TRUE}
library(fars)

file = make_filename(2013)
data = fars_read(file)
dim(data)
```

The data contains `r dim(data)[1]` observations and `r dim(data)[2]` attributes. Attentionally, `fars_read_years` won't return the raw data, instead return the list of dataset for each year containing only two attributes with 12 rows for each month in a year.

```{r echo=TRUE}
library(fars)
data = fars_read_years(2013:2014)

data[[1]]

```


## Summary accidents in years

To summerize accidents in years, user can use `fars_summarize_years(years)` with `years` that is either an integer vector or a string vector. `years` is valid for only a period ranging from 2013 to 2015.

```{r}
library(fars)
fars_summarize_years(2013:2015)
```
    
## Display the accident in a state of a particular year

To plot accidents of a state in a particular year, we will use `fars_map_state(state.num, year)`. `state.num` indicates the number for one state, while `year` indicates which year you want to plot. These arguments must be scala and can be either integer or string.

For an example, to display accident in the state 4 of the year 2013, we can invoke as the below:

```{r, echo=TRUE, results='asis'}
library(fars)
fars_map_state("4", "2013")
```

